---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hutchpalette

<!-- badges: start -->
<!-- badges: end -->

hutchpalette is a color palette package developed specifically for the Fred Hutchinson Cancer Center. This package leverages the power of [palettes](https://github.com/mccarthy-m-g/palettes/), an R package designed for working with color vectors and palettes.

The creation of hutchpalette was a straightforward process that involved following the step-by-step instructions outlined in the ["Creating a color palette package"](https://mccarthy-m-g.github.io/palettes/articles/creating-packages.html) vignette provided by the palettes R package. 

## Installation

You can install the development version of hutchpalette from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("howardbaek/hutchpalette")
```

## Using hutchpalette with ggplot2

Code borrowed from [Using palettes with ggplot2](https://mccarthy-m-g.github.io/palettes/articles/ggplot2.html)


```{r example}
library(hutchpalette)
library(ggplot2)
library(scales)
```


Show Fred Hutch colors

```{r}
plot(hutch_palette)
```


For discrete colors, use `scale_color_palette_d()`.

```{r}
ggplot(diamonds[sample(nrow(diamonds), 1000), ], aes(carat, price)) +
  geom_point(aes(colour = color)) +
  scale_colour_palette_d(hutch_palette)
```

Note that `hutch_palette` consists of only 7 colors, which means plotting a categorical variable with more than 7 distinct values will throw an error.

```{r, error = TRUE}
ggplot(diamonds[sample(nrow(diamonds), 1000), ], aes(carat, price)) +
  geom_point(aes(colour = clarity)) +
  scale_colour_palette_d(hutch_palette)
```

Continuous or binned colors can be used with continuous data. 

```{r}
hwy_mpg <- ggplot(mpg, aes(displ, hwy, colour = hwy)) +
  geom_point()
```


For continuous colors use `scale_color_palette_c()`. 

```{r}
hwy_mpg + scale_colour_palette_c(hutch_palette)
```


For binned colors use `scale_color_palette_b()`.

```{r}
hwy_mpg + scale_colour_palette_b(hutch_palette)
```

For discrete fills, use `scale_fill_palette_d()`.

```{r}
ggplot(diamonds, aes(x = price, fill = cut)) +
  geom_histogram(position = "dodge", binwidth = 1000) +
  scale_fill_palette_d(hutch_palette)
```

Continuous or binned fills can be used with continuous data.

```{r}
eruptions <- ggplot(faithfuld, aes(waiting, eruptions, fill = density)) +
  geom_tile()
```

For continuous fills use `scale_fill_palette_c()`. 

```{r}
eruptions + scale_fill_palette_c(hutch_palette)
```


For binned fills use `scale_fill_palette_b()`.

```{r}
eruptions + scale_fill_palette_b(hutch_palette)
```

